% !TeX spellcheck = en_US
%-------------------------
% Resume in Latex
% Author : Neil John D. Ortega
% License : MIT
%------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage{fontspec}
\usepackage{fontawesome5}
\usepackage[english]{babel}
\usepackage{tabularx}

\setmainfont{Roboto Light}

\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

%-------------------------
% Custom commands
\newcommand{\resumeSubheading}[4]{
  \vspace{-1pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small #3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-5pt}
}

\newcommand{\resumeSubheadingSubYear}[2]{
  \vspace{-1pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2
    \end{tabular*}\vspace{1pt}
}

\newcommand{\resumeSubSubHeading}[2]{
  \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
    \textit{\small{#1}} & \small{#2}
  \end{tabular*}\vspace{-8pt}
}

\newcommand{\resumeItem}[2]{
  \item\small{
    \textbf{#1}{\\ \begin{itemize}#2\end{itemize}\vspace{1pt}}
  }
}

\newcommand{\resumeItemInline}[2]{
  \item\small{
    \textbf{#1}{: #2 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubItem}[2]{\resumeItem{#1}{#2}\vspace{-4pt}}
\newcommand{\resumeSubItemInline}[2]{\resumeItemInline{#1}{#2}\vspace{-6pt}}

\renewcommand\labelitemii{$\vcenter{\hbox{$\bullet$}}$}
\renewcommand{\labelitemiii}{$\circ$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=*, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}\vspace{-5pt}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%------------------------------------------------------------------------------
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%  CV STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{document}

%----------------------------------- HEADING ----------------------------------
\begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
  \textbf{\Large Neil John D. Ortega} & \href{mailto:neiljohn.ortega@gmail.com}{neiljohn.ortega@gmail.com}\\
  \href{https://linkedin.com/in/neiljdo}{\faIcon{linkedin}\textnormal{ neiljdo}} | \href{https://github.com/neiljdo}{\faIcon{github}\textnormal{ neiljdo}} & +81-80-4629-2192 \\
\end{tabular*}


%--------------------------- SKILLS AND COMPETENCIES --------------------------
\section{Skills and Competencies}
  \resumeSubHeadingListStart
    \resumeSubItemInline{Soft Skills}
      {Strong work ethic, Strong verbal and written communication skills, Leadership and teamwork skills, Highly adaptable, Problem solver.}
    \resumeSubItemInline{Machine Learning and Deep Learning}
      {AutoGluon, AWS SageMaker, PyTorch, fastai, Keras, Tensorflow, scikit-learn, nltk, pandas, numpy, OpenCV, etc.}
    \resumeSubItemInline{Big Data}
      {Spark, Airflow, Redis, Kafka, Hive, Hadoop, etc.}
    \resumeSubItemInline{Full-Stack Development}
      {fastAPI, OpenAPI, Django, django-rest-framework, Flask, Shiny, D3.js, Front-end frameworks, etc.}
    \resumeSubItemInline{DevOps}
      {Docker, Kubernetes, Drone, Prometheus, Grafana, Jenkins, Ansible, AWS, etc.}
    \resumeSubItemInline{Scripting}
      {Python, R, SQL, Bash, etc.}
    \resumeSubItemInline{Collaboration and Project Management}
      {Git, JIRA, Confluence, Agile methodology, Scrum, etc.}
  \resumeSubHeadingListEnd


%--------------------------------- EXPERIENCE ---------------------------------
\section{Experience}
  \resumeSubHeadingListStart
    \resumeSubheading
    {Data Scientist}{Nov 2021 --- Present}
    {AI Cross Inc.}{Tokyo, Japan}
    \resumeItemListStart
      \resumeItem{Machine Learning Platform-as-a-Service}{
        \item Currently designing and implementing the core ML module of the platform that would allow users to train models and retrieve inference results via APIs.}
      
      \resumeItem{Business Marketing Platform-as-a-Service}{
        \item Developed prototype for generating and delivering AI-based recommendations in 1 month, allowing the team to pitch and present to potential clients and validate the value provided by the service.
        \item Created the system architecture for the product based on the initial prototype.
        \item Implemented data ingestion, model training, and recommendations generation components of the system, working across the entire stack (frontend, backend, ML module).
        \item Constantly communicated with the sales team to learn the client feedback and re-prioritize the development milestones accordingly.
        \item Implemented A/B testing feature that would allow businesses to experiment with their strategies and choose the best option within statistical bounds.
        \item Took the charge and self-learned about UI/UX to further improve the design of the platform.
        \item Collaborated with the CTO to create the pipeline for operationalizing the system.}
    \resumeItemListEnd

    \resumeSubheading
    {Machine Learning Engineer}{Sep 2019 --- Nov 2021}
    {LINE Fukuoka Corporation}{Fukuoka, Japan}
    \resumeItemListStart
      \resumeItem{Detection of High-Profile Individuals from Caricatures}{
        \item Benchmarked the performance of the existing tool we wanted to improve upon using Python scripts.
        \item Developed a detection approach based on the \href{https://arxiv.org/abs/1811.10100}{WarpGAN paper}.
        \item Implemented Spark, Airflow batch-processing pipeline that handles 1M image/s throughput.
        \item Developed and deployed APIs for real-time inference and visualization of batch detection results.
        \item Added service monitoring via Prometheus and Grafana to tighten the feedback loop in detecting target events.
        \item Wrote the entire deployment pipeline that allowed for faster iteration.}

      \resumeItem{Content Suggestion via Image-Based Emotion Recognition}{
        \item Coordinated with product team to scope the requirement.
        \item Designed model and solution architecture based on existing literature on \href{https://arxiv.org/abs/1608.01041}{emotion} \href{https://doi.org/10.3390/s18020401}{recognition}, \href{https://dl.acm.org/doi/10.1145/2959100.2959190}{recommendation} \href{https://arxiv.org/abs/1708.05031}{systems}.
        \item Trained baseline models for recognizing emotion from input images.
        \item Developed and deployed APIs for real-time inference.
        \item Implemented service monitoring via Prometheus and Grafana.}

      \resumeItem{Machine Learning Tooling and Knowledge-Sharing Tasks}{
        \item Worked with other members of the ML team to improve existing and/or create new ML/MLOps tools.
        \item Presented to the team the following areas of interest: meta-learning, \href{https://hackmd.io/@neiljdo/B1tXZUiCI}{model quantization \faIcon{link}}, \href{https://hackmd.io/@neiljdo/ByLImB9-u}{auto-ML \faIcon{link}}, \href{https://hackmd.io/@neiljdo/ByEk4H5WO}{causal inference \faIcon{link}}, \href{https://hackmd.io/@neiljdo/r1cP9fZh5}{secure AI \faIcon{link}}, and \href{https://hackmd.io/@neiljdo/HJ-XtKDzY}{explainable AI \faIcon{link}}.}
      \resumeItemListEnd

    \resumeSubheading
      {Data Scientist}{Nov 2016 --- Sep 2019}
      {Teradata Corporation}{Manila, Philippines}
      \resumeItemListStart
        \resumeItem{Data Extraction from Scanned Documents}{
          \item Trained random forest models and CNNs to improve the accuracy of predicting the location of fields of interest in documents.
          \item Developed ad-hoc scripts for rule-based detection and extraction of field values from documents.
          \item Improved image input to OCR service using OpenCV image preprocessing scripts.
          \item Extracted training data from scanned images using Tesseract and Microsoft OCR.}

        \resumeItem{Survey Response Classification}{
          \item Trained LSTM + word-embedding models using Keras with Tensorflow and scikit-learn for the classification of survey responses to easily diagnose problems the end-users are facing.
          \item Developed the end-to-end (E2E) solution architecture, closely collaborating with principal data scientist.
          \item Created an app for data ingestion and model results visualization using R, Python, and SQL that reduced manual labor and errors done by client.
          \item Streamlined both local and production deployment by writing a Docker pipeline.
          \item Hosted learning sessions for technologies the rest of the team are not familiar with.}

        \resumeItem{Customer Behavior Modeling}{
          \item Operationalized the models developed by data scientists via an ad-hoc parallelized Python pipeline.
          \item Tracked and fixed issues with the client's infrastructure, providing support to the client's Cloudera Cluster administrators.
          \item Benchmarked and optimized performance for both Hive data store and Teradata Aster compute engine that reduced E2E processing time from several days to 2-3 hours.}

        \resumeItem{Model Monitoring and Maintenance}{
          \item Created a Spark, Shiny application that allows users to run a scoring model against datasets in HDFS and visualize model health metrics.
          \item Determined high-value tasks and scoped the project, closely working with the client's analytics team.
          \item Deployed the entire solution via Ansible and Cloudera Manager on the customer's AWS cluster.
          \item Solution streamlined the customer's processes and reduced E2E processing time from 1 week to 1 hour.}

      \resumeItemListEnd

    \resumeSubheading
      {Senior Full-Stack Engineer}{Sep 2011 --- Nov 2016}
      {icannhas Inc.}{Manila, Philippines}
  \resumeSubHeadingListEnd


%---------------------------------- EDUCATION ---------------------------------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {Master of Science in Physics}{2021 --- Present}
      {\vspace{5pt}University of the Philippines Diliman, Quezon City. Expected completion: 2024}{}

    \resumeSubheading
      {Bachelor of Science in Civil Engineering, \textit{magna cum laude}}{2006 --- 2011}
      {\vspace{5pt}University of the Philippines Diliman, Quezon City}{}
      \small Awardee, Engineering Top 100 in Academics, 2011 (out of 5000 students) \\
      \small 10th Place, ACM International Collegiate Programming Contest Asia Manila Regional Contest, 2009 \\
      \small Honorable Mention, 37th International Physics Olympiad, 2006
  \resumeSubHeadingListEnd

%---------------------------------- CERTIFICATES ---------------------------------
\section{Certificates}
  \resumeSubHeadingListStart
    \resumeSubheading
      {2022 Qiskit Global Summer School on Quantum Simulations}{2022}
      {\vspace{5pt}Online course. Expected completion: July 29, 2022}{}
    \resumeSubheading
      {2021 Qiskit Global Summer School on Quantum Machine Learning}{2021}
      {\vspace{5pt}Online course.}{}
  \resumeSubHeadingListEnd

%------------------------- ACTIVITIES / ORGANIZATIONS -------------------------
% \section{Activities and Organizations}
%   \resumeSubHeadingListStart
%     \resumeSubheadingSubYear
%       {University of the Philippines Tennis Society}{}
%       \resumeSubSubHeading{Secretary-General for Special Events}{2009 --- 2010}
%       \resumeItemListStart
%         \item{Headed committee responsible for teaching tennis to future and current members and in handling the logistics of events.}
%         \item{Spearheaded annual university-wide tournament hosted by the organization. Lead the entire organization of 50+ members, coordinated with sponsors and participants to ensure the success of the annual event.}
%       \resumeItemListEnd
%   \resumeSubHeadingListEnd


%------------------------------------------------------------------------------
\end{document}
